PhD Notebook

### 2022-03-06 site/02-literature-vi.Rmd
update 2

# Literature

@@

[comment]: <> (What is the probability of the true plot be the most different one?)

[comment]: <> (What is the probability of the first plot be the most different one? == What is the probability of the second plot be the most different one?)

@@

>>>>

# Literature - Visual Inference

@@

@@

## Statistical inference for exploratory data analysis and model diagnostics

BibTex: 
```
@article{buja2009statistical,
  title={Statistical inference for exploratory data analysis and model diagnostics},
  author={Buja, Andreas and Cook, Dianne and Hofmann, Heike and Lawrence, Michael and Lee, Eun-Kyung and Swayne, Deborah F and Wickham, Hadley},
  journal={Philosophical Transactions of the Royal Society A: Mathematical, Physical and Engineering Sciences},
  volume={367},
  number={1906},
  pages={4361--4383},
  year={2009},
  publisher={The Royal Society Publishing}
}
```

permutation tests, rotation tests, statistical graphics, visual data mining, simulation, cognitive perception.

# Introduction

### 2022-03-06 site/_book/site.tex
update 2

\title{PhD Notebook}
\author{Patrick Li}
\date{2021-06-20}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  records of weekly meetings
\item
  literature review
\item
  to-do list
\item
  milestones
\item
  links to resources
\end{enumerate}

\hypertarget{literature}{%
\chapter{Literature}\label{literature}}

@@

\hypertarget{meetings}{%
\chapter{Meetings}\label{meetings}}

\hypertarget{march-10-2021---week-2}{%
\section{March 10, 2021 - Week 2}\label{march-10-2021---week-2}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Human subject experiment and Monash permission

  \begin{itemize}
  \tightlist
  \item
    There is a workshop in May
  \end{itemize}
\item
  Use simulated data to set up an experiment
\item
  Check out Gallery of graphs (a name yan \ldots{} not sure)
\item
  The experiment could start from residual plot
\item
  Q-Q plot could also be considered
\item
  A revelant research - residual calculation by kaiwen - master project
\item
  Use Appen survey to collect data
\item
  Build a Github to-do list, meeting record and summary of the literature
\item
  There may be some development in the theory by Nancy Reid - theoretical statistician (recent work)
\item
  Consider using Kears to build a computer vision model
\end{enumerate}

\hypertarget{march-17-2021---week-3}{%
\section{March 17, 2021 - Week 3}\label{march-17-2021---week-3}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Read Susan Vanderplas's personal website to find additional information
\item
  Check out NUMBAT residual plot comparision - summer-vis-inf : Aarathy Babu - code examples
\item
  Read human subject premission examples (sent by Di)
\item
  Check out top-up application
\item
  Consider to use \texttt{Edibble} to set up the experiment
\item
  Build the PhD repo
\item
  Consider to use non-shiny framework
\end{enumerate}

\hypertarget{march-21-2021---week-4}{%
\section{March 21, 2021 - Week 4}\label{march-21-2021---week-4}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A short meeting - late for 30 minutes
\item
  Aarathy introduces her repo
\end{enumerate}

\hypertarget{march-28-2021---week-5}{%
\section{March 28, 2021 - Week 5}\label{march-28-2021---week-5}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Discuss the options of building a alternative hypothesis in residual plot
\item
  AR, heterogeneity of variance, endogeneity, skewness, exp distribution, poisson distribution and missing covariance
\item
  Choice of plot design (loess or \(y=0\) line), number of lineup (5\textasciitilde15), number of observations
\item
  Use flow chart to illustrate the choices
\item
  Literature review - check previous designs
\item
  Build bookdown to track records
\end{enumerate}

\hypertarget{todo}{%
\chapter{TODO}\label{todo}}

\hypertarget{week-3}{%
\section{Week 3}\label{week-3}}

\begin{itemize}
\tightlist
\item[$\boxtimes$]
  Check human subject experiment and Monash permission materials

  \begin{itemize}
  \tightlist
  \item
    \url{https://www.intranet.monash/researchadmin/start/ethics/human}
  \end{itemize}
\item[$\boxtimes$]
  Check Kaiwen's project \& paper
\item[$\square$]
  Check Gallery of graphs - unclear author
\end{itemize}

\hypertarget{week-4}{%
\section{Week 4}\label{week-4}}

\begin{itemize}
\tightlist
\item[$\boxtimes$]
  Build prototype of html webpage to collect data
\item[$\boxtimes$]
  Send data to google sheet
\item[$\boxtimes$]
  Check summer-vis-inf
\item[$\boxtimes$]
  Read examples sent by Di
\item[$\square$]
  Build PhD repo

  \begin{itemize}
  \tightlist
  \item[$\boxtimes$]
    meetings
  \item[$\square$]
    paper
  \item[$\boxtimes$]
    TODO
  \end{itemize}
\item[$\square$]
  Check Susan Vanderplas's website

  \begin{itemize}
  \tightlist
  \item[$\square$]
    paper
  \item[$\square$]
    talks
  \item[$\square$]
    posts
  \end{itemize}
\end{itemize}

\hypertarget{week-5}{%
\section{Week 5}\label{week-5}}

\begin{itemize}
\tightlist
\item[$\boxtimes$]
  modify the webpage to be able to select multiple plots
\item[$\boxtimes$]
  Attempt to generate data from one assumed model
\item[$\square$]
  draft Human Ethics Application Form
\end{itemize}

\hypertarget{week-6}{%
\section{Week 6}\label{week-6}}

\begin{itemize}
\tightlist
\item[$\square$]
  Do the literature review of previous design
\item[$\square$]
  Draw a flow chart to illustrate the design
\end{itemize}

>>>>

\title{PhD Notebook}
\author{Patrick Li}
\date{2022-01-14}

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  records of weekly meetings
\item
  literature review
\item
  TO-DO list
\item
  milestones
\item
  links to resources
\end{enumerate}

\hypertarget{literature---visual-inference}{%
\chapter{Literature - Visual Inference}\label{literature---visual-inference}}

@@

\hypertarget{statistical-inference-for-exploratory-data-analysis-and-model-diagnostics}{%
\section{Statistical inference for exploratory data analysis and model diagnostics}\label{statistical-inference-for-exploratory-data-analysis-and-model-diagnostics}}

\hypertarget{literature---computer-vision}{%
\chapter{Literature - Computer vision}\label{literature---computer-vision}}
